\textbf{Supplementary Information}

### 2020-03-19 submission/supplementary.tex
Analysis rerun.
Pipeline optimization.

\caption{Rarefaction curves of bacterial and archaeal communities from the surfaces of macrophytes (\textit{C. nodosa} [Invaded] and \textit{C. cylindracea} [Invaded and Noninvaded]) and in the ambient seawater.\label{rarefaction}}\label{fig:unnamed-chunk-1}
\end{figure}

@@

\caption{Seasonal dynamics of observed number of OTUs, Chao1, ACE, exponential of the Shannon Diversity Index and Inverse Simpson Index of bacterial and archaeal communities from the surfaces of macrophytes (\textit{C. nodosa} [Invaded] and \textit{C. cylindracea} [Invaded and Noninvaded]) and in the ambient seawater.\label{calculators}}\label{fig:unnamed-chunk-2}
\end{figure}

@@

\caption{Relative contribution of chloroplast sequences on the surfaces of macrophytes (\textit{C. nodosa} [Invaded] and \textit{C. cylindracea} [Invaded and Noninvaded]) and in the ambient seawater.\label{chloroplast}}\label{fig:unnamed-chunk-3}
\end{figure}

@@

\begin{longtable}{>{\centering\arraybackslash}p{6em}ccccc}

@@

3 & Seawater & 13 July 2017 & Summer & 26,008 & 824\\
5 & Seawater & 27 July 2017 & Summer & 58,955 & 993\\
7 & Seawater & 10 August 2017 & Summer & 32,626 & 852\\
9 & Seawater & 24 August 2017 & Summer & 60,929 & 1,058\\
11 & Seawater & 19 September 2017 & Summer & 46,111 & 1,171\\
13 & Seawater & 12 October 2017 & Autumn & 30,937 & 976\\
15 & Seawater & 23 November 2017 & Autumn & 27,581 & 1,183\\
17 & Seawater & 14 December 2017 & Autumn & 44,595 & 2,267\\
19 & Seawater & 13 February 2018 & Winter & 44,186 & 1,309\\
21 & Seawater & 27 March 2018 & Winter & 46,307 & 1,559\\
23a & Seawater & 24 April 2018 & Spring & 30,970 & 998\\
23b & Seawater & 24 April 2018 & Spring & 38,560 & 1,200\\
25 & Seawater & 22 May 2018 & Spring & 53,880 & 1,783\\
27 & Seawater & 19 June 2018 & Spring & 77,465 & 1,297\\
29 & Seawater & 10 July 2018 & Summer & 50,794 & 1,451\\
31 & Seawater & 9 August 2018 & Summer & 39,049 & 1,129\\
33 & Seawater & 4 September 2018 & Summer & 36,206 & 1,205\\
35 & Seawater & 5 October 2018 & Autumn & 49,580 & 1,013\\
37 & \textit{Cymodocea nodosa} (Invaded) & 23 November 2017 & Autumn & 31,235 & 1,548\\
41 & \textit{Cymodocea nodosa} (Invaded) & 4 December 2017 & Autumn & 24,237 & 1,176\\
45 & \textit{Cymodocea nodosa} (Invaded) & 14 December 2017 & Autumn & 32,683 & 1,051\\
49 & \textit{Cymodocea nodosa} (Invaded) & 13 February 2018 & Winter & 9,087 & 1,218\\
52 & \textit{Cymodocea nodosa} (Invaded) & 27 March 2018 & Winter & 17,003 & 1,218\\
55 & \textit{Cymodocea nodosa} (Invaded) & 24 April 2018 & Spring & 42,640 & 2,054\\
58 & \textit{Cymodocea nodosa} (Invaded) & 22 May 2018 & Spring & 21,337 & 1,292\\
61 & \textit{Cymodocea nodosa} (Invaded) & 19 June 2018 & Spring & 31,735 & 2,104\\
64 & \textit{Cymodocea nodosa} (Invaded) & 10 July 2018 & Summer & 35,733 & 1,792\\
67 & \textit{Cymodocea nodosa} (Invaded) & 9 August 2018 & Summer & 26,362 & 2,119\\
70 & \textit{Cymodocea nodosa} (Invaded) & 4 September 2018 & Summer & 23,278 & 1,715\\
73 & \textit{Cymodocea nodosa} (Invaded) & 5 October 2018 & Autumn & 29,909 & 2,205\\
38 & \textit{Caulerpa cylindracea} (Invaded) & 23 November 2017 & Autumn & 36,321 & 2,889\\
42 & \textit{Caulerpa cylindracea} (Invaded) & 4 December 2017 & Autumn & 28,370 & 3,249\\
46 & \textit{Caulerpa cylindracea} (Invaded) & 14 December 2017 & Autumn & 34,720 & 3,054\\
53 & \textit{Caulerpa cylindracea} (Invaded) & 27 March 2018 & Winter & 28,696 & 2,472\\
56 & \textit{Caulerpa cylindracea} (Invaded) & 24 April 2018 & Spring & 34,773 & 3,054\\
59 & \textit{Caulerpa cylindracea} (Invaded) & 22 May 2018 & Spring & 23,397 & 2,706\\
62 & \textit{Caulerpa cylindracea} (Invaded) & 19 June 2018 & Spring & 36,477 & 3,299\\
65 & \textit{Caulerpa cylindracea} (Invaded) & 10 July 2018 & Summer & 18,485 & 2,188\\
68 & \textit{Caulerpa cylindracea} (Invaded) & 9 August 2018 & Summer & 31,940 & 3,103\\
71 & \textit{Caulerpa cylindracea} (Invaded) & 4 September 2018 & Summer & 29,281 & 3,160\\
74 & \textit{Caulerpa cylindracea} (Invaded) & 5 October 2018 & Autumn & 11,705 & 1,705\\
39 & \textit{Caulerpa cylindracea} (Nonnvaded) & 23 November 2017 & Autumn & 22,064 & 2,438\\
43 & \textit{Caulerpa cylindracea} (Nonnvaded) & 4 December 2017 & Autumn & 13,661 & 1,887\\
47 & \textit{Caulerpa cylindracea} (Nonnvaded) & 14 December 2017 & Autumn & 8,410 & 1,451\\
51 & \textit{Caulerpa cylindracea} (Nonnvaded) & 13 February 2018 & Winter & 11,676 & 1,901\\
54 & \textit{Caulerpa cylindracea} (Nonnvaded) & 27 March 2018 & Winter & 39,472 & 3,136\\
57 & \textit{Caulerpa cylindracea} (Nonnvaded) & 24 April 2018 & Spring & 20,298 & 2,822\\
60 & \textit{Caulerpa cylindracea} (Nonnvaded) & 22 May 2018 & Spring & 33,047 & 3,297\\
63 & \textit{Caulerpa cylindracea} (Nonnvaded) & 19 June 2018 & Spring & 41,833 & 3,968\\
66 & \textit{Caulerpa cylindracea} (Nonnvaded) & 10 July 2018 & Summer & 27,036 & 2,674\\
69 & \textit{Caulerpa cylindracea} (Nonnvaded) & 9 August 2018 & Summer & 26,737 & 3,130\\
72 & \textit{Caulerpa cylindracea} (Nonnvaded) & 4 September 2018 & Summer & 31,869 & 3,240\\
75 & \textit{Caulerpa cylindracea} (Nonnvaded) & 5 October 2018 & Autumn & 33,068 & 3,086\\*

>>>>

\caption{Rarefaction curves of bacterial and archaeal communities from the surfaces of macrophytes (\textit{C. nodosa} [Mixed] and \textit{C. cylindracea} [Mixed and Monospecific]) and in the ambient seawater.\label{rarefaction}}\label{fig:unnamed-chunk-1}
\end{figure}

@@

\caption{Seasonal dynamics of observed number of OTUs, Chao1, ACE, exponential of the Shannon Diversity Index and Inverse Simpson Index of bacterial and archaeal communities from the surfaces of macrophytes (\textit{C. nodosa} [Mixed] and \textit{C. cylindracea} [Mixed and Monospecific]) and in the ambient seawater.\label{calculators}}\label{fig:unnamed-chunk-2}
\end{figure}

@@

\caption{Relative contribution of chloroplast sequences on the surfaces of macrophytes (\textit{C. nodosa} [Mixed] and \textit{C. cylindracea} [Mixed and Monospecific]) and in the ambient seawater.\label{chloroplast}}\label{fig:unnamed-chunk-3}
\end{figure}

@@

\begin{longtable}[t]{>{\centering\arraybackslash}p{6em}ccccc}

@@

3 & Seawater & 13 July 2017 & Summer & 25,996 & 821\\
5 & Seawater & 27 July 2017 & Summer & 58,954 & 993\\
7 & Seawater & 10 August 2017 & Summer & 32,626 & 853\\
9 & Seawater & 24 August 2017 & Summer & 60,935 & 1,064\\
11 & Seawater & 19 September 2017 & Summer & 46,107 & 1,179\\
13 & Seawater & 12 October 2017 & Autumn & 30,911 & 971\\
15 & Seawater & 23 November 2017 & Autumn & 27,585 & 1,197\\
17 & Seawater & 14 December 2017 & Autumn & 44,595 & 2,275\\
19 & Seawater & 13 February 2018 & Winter & 44,207 & 1,306\\
21 & Seawater & 27 March 2018 & Winter & 46,313 & 1,561\\
23a & Seawater & 24 April 2018 & Spring & 30,973 & 999\\
23b & Seawater & 24 April 2018 & Spring & 38,563 & 1,195\\
25 & Seawater & 22 May 2018 & Spring & 53,877 & 1,787\\
27 & Seawater & 19 June 2018 & Spring & 77,465 & 1,290\\
29 & Seawater & 10 July 2018 & Summer & 50,793 & 1,445\\
31 & Seawater & 9 August 2018 & Summer & 39,041 & 1,123\\
33 & Seawater & 4 September 2018 & Summer & 36,206 & 1,206\\
35 & Seawater & 5 October 2018 & Autumn & 49,585 & 1,019\\
37 & \textit{Cymodocea nodosa} (Mixed) & 23 November 2017 & Autumn & 31,237 & 1,555\\
41 & \textit{Cymodocea nodosa} (Mixed) & 4 December 2017 & Autumn & 24,234 & 1,174\\
45 & \textit{Cymodocea nodosa} (Mixed) & 14 December 2017 & Autumn & 32,683 & 1,061\\
49 & \textit{Cymodocea nodosa} (Mixed) & 13 February 2018 & Winter & 9,088 & 1,216\\
52 & \textit{Cymodocea nodosa} (Mixed) & 27 March 2018 & Winter & 17,005 & 1,216\\
55 & \textit{Cymodocea nodosa} (Mixed) & 24 April 2018 & Spring & 42,645 & 2,053\\
58 & \textit{Cymodocea nodosa} (Mixed) & 22 May 2018 & Spring & 21,337 & 1,290\\
61 & \textit{Cymodocea nodosa} (Mixed) & 19 June 2018 & Spring & 31,726 & 2,098\\
64 & \textit{Cymodocea nodosa} (Mixed) & 10 July 2018 & Summer & 35,729 & 1,793\\
67 & \textit{Cymodocea nodosa} (Mixed) & 9 August 2018 & Summer & 26,356 & 2,116\\
70 & \textit{Cymodocea nodosa} (Mixed) & 4 September 2018 & Summer & 23,275 & 1,724\\
73 & \textit{Cymodocea nodosa} (Mixed) & 5 October 2018 & Autumn & 29,907 & 2,211\\
38 & \textit{Caulerpa cylindracea} (Mixed) & 23 November 2017 & Autumn & 36,309 & 2,896\\
42 & \textit{Caulerpa cylindracea} (Mixed) & 4 December 2017 & Autumn & 28,383 & 3,249\\
46 & \textit{Caulerpa cylindracea} (Mixed) & 14 December 2017 & Autumn & 34,718 & 3,067\\
53 & \textit{Caulerpa cylindracea} (Mixed) & 27 March 2018 & Winter & 28,689 & 2,481\\
56 & \textit{Caulerpa cylindracea} (Mixed) & 24 April 2018 & Spring & 34,784 & 3,057\\
59 & \textit{Caulerpa cylindracea} (Mixed) & 22 May 2018 & Spring & 23,392 & 2,712\\
62 & \textit{Caulerpa cylindracea} (Mixed) & 19 June 2018 & Spring & 36,488 & 3,311\\
65 & \textit{Caulerpa cylindracea} (Mixed) & 10 July 2018 & Summer & 18,483 & 2,188\\
68 & \textit{Caulerpa cylindracea} (Mixed) & 9 August 2018 & Summer & 31,943 & 3,097\\
71 & \textit{Caulerpa cylindracea} (Mixed) & 4 September 2018 & Summer & 29,273 & 3,152\\
74 & \textit{Caulerpa cylindracea} (Mixed) & 5 October 2018 & Autumn & 11,707 & 1,711\\
39 & \textit{Caulerpa cylindracea} (Monospecific) & 23 November 2017 & Autumn & 22,057 & 2,428\\
43 & \textit{Caulerpa cylindracea} (Monospecific) & 4 December 2017 & Autumn & 13,661 & 1,892\\
47 & \textit{Caulerpa cylindracea} (Monospecific) & 14 December 2017 & Autumn & 8,409 & 1,451\\
51 & \textit{Caulerpa cylindracea} (Monospecific) & 13 February 2018 & Winter & 11,673 & 1,899\\
54 & \textit{Caulerpa cylindracea} (Monospecific) & 27 March 2018 & Winter & 39,471 & 3,142\\
57 & \textit{Caulerpa cylindracea} (Monospecific) & 24 April 2018 & Spring & 20,304 & 2,836\\
60 & \textit{Caulerpa cylindracea} (Monospecific) & 22 May 2018 & Spring & 33,035 & 3,314\\
63 & \textit{Caulerpa cylindracea} (Monospecific) & 19 June 2018 & Spring & 41,841 & 3,976\\
66 & \textit{Caulerpa cylindracea} (Monospecific) & 10 July 2018 & Summer & 27,038 & 2,669\\
69 & \textit{Caulerpa cylindracea} (Monospecific) & 9 August 2018 & Summer & 26,734 & 3,123\\
72 & \textit{Caulerpa cylindracea} (Monospecific) & 4 September 2018 & Summer & 31,874 & 3,248\\
75 & \textit{Caulerpa cylindracea} (Monospecific) & 5 October 2018 & Autumn & 33,073 & 3,078\\*
